### 2016-05-20 intro.tex
I am now convinced that their syntax does *not* capture real Bloom filters.  I added a note to argue this even more forcefully than before :)

>>>>

\tsnote{UPDATE (5/20/16): I'm now convinced that what they call memory size~$m$, when applied to real Bloom filters, is \emph{only} the size of the bit array, and does \emph{not} include a description of the hash functions.  The memory size comparisons that are made throughout the paper are to classical memory lowerbounds that account only for the bitsize of the array. Concretely: in the abstract they say ``... we show thre exists a Bloom filter for sets of size~$n$ and error~$\epsilon$ , that is secure against~$t$ queries and uses only $O(n\log\frac{1}{\varepsilon} + t)$ bits of memory.  In comparison, $n \log\frac{1}{\varepsilon}$ is the best possible under a non-adaptive adversary.''  The latter bound is the classical one.   If you look in the paper for this actual result, it's in Theorem 6.2.   So, we look at the theorem and the construction that proves it.  It uses a specially constructed function~$g$ and a Cuckoo hashing dictionary~$D$, consisting of two tables~$T_1,T_2$ and two hash functions~$h_1,h_2$.  Here is a quote from the proof ``The final memory of the Bloom filter is the memory of~$D$ and the representation of~$g$.  The dictionary~$D$ consists of $O(n)$ cells, each of size $|g(x)|=O(\log\frac{1}{\varepsilon})$ bits and therefore~$D$ and~$g$ together can be represented using $O(n\log\frac{1}{\varepsilon} + t)$ bits'', where earlier they say ``the representation of~$g$ requires $O(t)$ bits''.  Thus they are \emph{not} considering the size of the hash functions~$h_1,h_2$ that are used to populate the cells of~$D$.   So, as I said, I'm now convinced that their Bloom filter syntax does not actually capture real Bloom filters.}
